---
title: "p8105_hw6_rd3097"
output: html_document
date: "2023-12-03"
---

Necessary Library
```{r}
library(tidyverse)
library(modelr)
library(rnoaa)

```

### Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

```{r}
#First we focus on estimate of r squared
weather_fit <- weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin+prcp, data = .x) ),
    tidy   = map(models, broom::tidy),
    glance = map(models, broom::glance)) %>%
  select(-strap, -models)

r_squared_estimate<-weather_fit%>%
  select(-tidy) %>%
  unnest(glance)%>%
  select(.id, r.squared)

r_squared_estimate%>%
  ggplot(aes(x = r.squared))+geom_density()

r_square<- r_squared_estimate%>%
summarize(r_squared_lower = quantile(r.squared, 0.025),
  r_squared_upper = quantile(r.squared, 0.975))
                      
```
From the r squared distribution graph, we can see it looks a little bit left skewed, and it has mean `r mean(pull(r_squared_estimate, r.squared))` and standard deviation `r sd(pull(r_squared_estimate, r.squared))`. The 95% confidence interval for r squared is `r pull(r_square, r_squared_lower)` to `r pull(r_square, r_squared_upper)`
```{r}
#Then we produce estimate for log beta0 * beta 1

beta_estimate <- weather_fit%>%
  select(-glance)%>%
  unnest(tidy)%>%
  select(.id, term, estimate)%>%
  pivot_wider(names_from = term,
              values_from = estimate)%>%
  rename(beta_0 = `(Intercept)`,
         beta_1 = tmin)%>%
  mutate(
    logb0b1 = log(beta_0*beta_1))%>%
  select(logb0b1)

beta_estimate%>%
  ggplot(aes(x = logb0b1))+geom_density()


beta<-beta_estimate%>%
  summarize(beta_lower = quantile(logb0b1, 0.025),
  beta_upper = quantile(logb0b1, 0.975))
```
From the log(b0*b1) graph, we can see it is normally distributed with mean of
`r mean(pull(beta_estimate, logb0b1))` and standard deviation `r sd(pull(beta_estimate, logb0b1))`. The confidence interval is ( `r pull(beta, beta_lower)` , `r pull(beta, beta_upper)` ).

### Problem 3

```{r}
read_csv("birthweight.csv")
```

